---
title: "Homework 6"
author: "Murrel Pereira"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

Find some residuals

Load data
```{r}
baby_df = 
  read_csv("./data/birthweight.csv")
```

```{r}
baby_df = 
  baby_df %>% 
  mutate(
    babysex = as.factor(babysex),
   # bwt = as.factor(bwt),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace),
    parity = as.factor(parity),
    pnumlbw = as.factor(pnumlbw),
    pnumsga = as.factor(pnumsga)
  )
```

Proposed Model
```{r}
model_fit_proposal = lm(bwt ~ bhead + blength + babysex + gaweeks + mrace + fincome + smoken + ppbmi + bhead*babysex + blength*babysex + bhead*blength*babysex , data = baby_df)

model_fit_proposal %>% 
  broom::tidy() %>% 
  knitr::kable()
```

I picked this model by doing backwards stepwise with all main effects and interactions/three-way intractions for `blength`, `bhead`, and `babysex`. I used the criteria that the p-value had to be less than 0.05 for the model. Many of the physical characteristics of the baby (`bhead`, `blength`, `babysex`, `gaweeks`) and mom health and socioeconomic factors (`mrace`, `fincome`, `smoken`, `ppbmi`) made it into the model. Factors with just one level (`pnumsga` and `pnumlbw`) were not incorporated since these factors didn't have enough levels.

```{r}
baby_df %>% 
  modelr::add_residuals(model_fit_proposal) %>% 
  modelr::add_predictions(model_fit_proposal) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

When looking at the residuals versus and predictions plot for the model, we notice that the residuals are spread evenly around 0 when the bwt prediction is above 2000 g. There might be some points under this weight that are outliers or cannot be explained by the factors in the model.

```{r}
cv_baby_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    model_fit_proposal = map(train, ~lm(bwt ~ bhead + blength + babysex + gaweeks + mrace + fincome + smoken + ppbmi + bhead*babysex + blength*babysex + bhead*blength*babysex , data = .x)),
    model_fit_a  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    model_fit_b  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, sp = 10e-6, data = .x))
    ) %>% 
  mutate(
    rmse_proposal = map2_dbl(model_fit_proposal, test, ~rmse(model = .x, data = .y)),
    rmse_fit_a = map2_dbl(model_fit_a, test, ~rmse(model = .x, data = .y)),
    rmse_fit_b = map2_dbl(model_fit_b, test, ~rmse(model = .x, data = .y))    
  ) 
```

This graph compares the models to each other. As you can see from the RMSE plots, the proposed model has the lowest RMSE compared to model A and model B. 
```{r}
cv_baby_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}

```

